---
title: "R Notebook"
output: html_notebook
---


```{r}
library(tidyverse)
library(dsbox)

```



### Exercise 1. What are the three most common first names of purchasers?

```{r}
lego_sales %>% 
  count(first_name) %>%
  arrange(desc(n)) %>%
  head(3)
```
  - #### Answer: The first three common first names of purchasers are ‘Jackson', 'Jacob', and 'Joseph'.


### Exercise 2. What are the three most common themes of Lego sets purchased?

```{r}
lego_sales %>% 
  count(theme) %>%
  arrange(desc(n)) %>%
  head(3)
```
  - #### Answer: The top three most common themes are 'Star Wars', 'Nexo Knights', and 'Gear'.
  

### Exercise 3. Among the most common theme of Lego sets purchased, what is the most common subtheme?

```{r}
lego_sales %>% 
  filter(theme == "Star Wars") %>%
  count(subtheme) %>%
  arrange(desc(n)) %>%
  head(1)
```
  - #### Answer: Among the most common theme of Lego (which is 'Star Wars'), 'The Force Awakens' is the most common subtheme. 
  
  
### Exercise 4. Create a new variable called age_group and group the ages into the following categories: “18 and under”, “19 - 25”, “26 - 35”, “36 - 50”, “51 and over”.

```{r}
lego_sales %>%
  mutate(age_group = case_when(age <= 18 ~ "18 and under", 
                               age >= 19 & age <= 25 ~ "19 - 25", 
                               age >= 26 & age <= 35 ~ "26 - 35", 
                               age >= 36 & age <= 50 ~ "36 - 50", 
                               age >= 51 ~ "51 and over"
  ))
```

### Exercise 5. Which age group has purchased the highest number of Lego sets.

```{r}
lego_sales %>%
  group_by(age_group) %>%
  summarise(total = sum(quantity)) %>%
  arrange(desc(total))
```

  - #### Answer: Ages that between 36 and 50 years old has purchuased the highest number of lege sets (313).
  

### Exercise 6. Which age group has spent the most money on Legos?

```{r}
lego_sales %>%
  group_by(age_group) %>%
  summarise(total_money = sum(us_price * quantity)) %>%
  arrange(desc(total_money))
```

  - #### Answer: Age group 36-50 has spent the most money on Legos.
  
  
### Exercise 7. Which Lego theme has made the most money for Lego?

```{r}
lego_sales %>%
  group_by(theme) %>%
  summarise(total_price = sum(us_price * quantity)) %>%
  arrange(desc(total_price))
```
  - #### Answer: Star Wars has made the most money for Lego


### Exercise 8. Which area code has spent the most money on Legos? In the US the area code is the first 3 digits of a phone number.

```{r}
lego_sales %>%
  group_by(str_sub(phone_number,1, 3)) %>%
  summarise(total_spend = sum(us_price * quantity)) %>%
  arrange(desc(total_spend))
```
  - #### Answer: Area code '956' has spent the most money on Legos.
  

#### Exercise 9. Come up with a question you want to answer using these data, and write it down. Then, create a data visualization that answers the question, and explain how your visualization answers the question.


  - #### My question: Which theme is the most popular among different age groups?
  
```{r}
lego_sales %>%
  group_by(age_group) %>%
  count(theme) %>%
  arrange(desc(n))

ggplot(data = lego_sales, mapping = aes(y = theme)) + geom_bar() + facet_wrap(~age_group, nrow = 1)
```
  
  - #### Answer: According to the visualization, I can see that 'City' is the most popular theme for age 18 and under; 'Nexo Knights' is the most popular for age 19-25; Star Wars is the most popular for age 26-35, and so does for age 36-50, and 51 and above.


